Networked Character Devices

### 2011-12-11 report/paper.tex
paper: ncadmin subsection

>>>>

\lstinputlisting[
  caption={The potential management interface for the NCD system.},
  label=lst:ncadmin
]{ncadmin.txt}

As NCD grows, it will be important for the client to be able to handle
dynamically added and removed devices. Listing \ref{lst:ncadmin}
provides an idea of what an interface would look like to provide such
functionality. This would give NCD the ability to create its character
devices anywhere under \texttt{/dev}; they could be placed in a similar
location to the corresponding device on the server.
